\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 bmc_section.tex
.

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}{vdp-graph}
\begin{example}
    Coming back to~\exref{vdp}, \figref{vdp-graph} %and\tabref{vdp-pwa}
    shows the abstract reachability graph with its transition
    relations. The relational maps are omitted for brevity.
    Note that self loops result when an observed trajectory
    segment begins and ends in the same cell.
    The graph $\scr{H}(0.1)$ can now be viewed as a
    transition system $\tupleof{C,\x,\scrT,C_0,\HybridStates_0}$,
    where $C \in vertices(\scr{H}(0.1))$ and $\x \in
    \HybridStates$. A transition $\tau \in \scrT$ is of the form
    $\tupleof{C, C',\rho_{\tau}}$, where $\rho_{\tau}(\x,\x')
    \subseteq \setof{R_{(C,C')}(\x,\x') |( C,C') \in
    edge(\scr{H}(0.1))}$.

>>>>

\inclfig[width=0.50\linewidth]{vdp_graph.pdf}{$\epsilon$-RTS for the
Van der Pol abstraction. Each edge corresponds to an affine map $F$
and summarizes the transition relation.}{vdp-graph}
\begin{example}
    Coming back to~\exref{vdp}, \figref{vdp-graph} %and\tabref{vdp-pwa}
    shows the abstract reachability graph with its transition
    relations. The relational maps are omitted for brevity.
    Note that self loops result when an observed trajectory
    segment begins and ends in the same cell.
    The graph $\scr{H}(0.1)$ can now be viewed as a
    transition system $\tupleof{C,\x,\scrT,C_0,\HybridStates_0}$,
    where $C \in vertices(\scr{H}(0.1))$ and $\x \in
    \HybridStates$. A transition $\tau \in \scrT$ is of the form
    $\tupleof{C, C',\rho_{\tau}}$, where $\rho_{\tau}(\x,\x')
    \subseteq \setof{R_{(C,C')}(\x,\x') |( C,C') \in
    edge(\scr{H}(0.1))}$.
